---
title: "GIMME Cutoff Simulation"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

This document contains code for a small simulation on using different fit index cutoffs
as stopping criteria for GIMME. 

# Preparation
```{r packages}
library(mvgimme)    # multiverse gimme
library(SimDesign)  # simulation design

```

Reproducibility
```{r reproducibility}
set.seed(35037)
```





# Simulation settings
Create a design with different sample sizes and time series lengths.
```{r sim-settings}
sample_sizes <- c(50, 100, 200)
ts_lengths <- c(50, 100, 200)

sim_design <- SimDesign::createDesign(sample_size = sample_sizes,
                                  ts_length = ts_lengths)

```

Fixed parameters across simulations: Data-Generating processes. 



# Data Generation
First, obtain "true" network from empirical data. 
```{r true-dgp}

```



Then, create data-generation function to sample from this model, using `gimme`. 
```{r data-generation}
sim_generate <- function(condition, fixed_objects = NULL){
  n <- condition$sample_size
  t <- condition$ts_length
  
  # obtain fixed parameters
  # TODO
  
  mvgimme::simulateVAR()
  
}
```




# Fitting functions
We use standard GIMME, and 3 different threshold methods in mvgimme. 
```{r fitting-methods}
sim_analyse_gimme <- function(condition, dat, fixed_objects = NULL){
  
  
}
```



# Summary function
```{r summary-function}

```




# Execute Simulation

```{r}
SimDesign::runSimulation(sim_design, replications = 1000, store_results = TRUE, 
                         generate = sim_generate, 
                         analyse = list(gimme = sim_analyse_gimme, 
                                        threshold = sim_analyse_threshold), 
                         summarise = sim_summarise, save = TRUE, save_seeds = TRUE,
                         packages = c("gimme"), fixed_objects = sim_pars)
```



# Evaluation
